Learning Augmented Joint-Space Task-Oriented Dynamical Systems: \\ A Linear Parameter Varying and Synergetic Control Approach

### 2017-10-28 paper/main_RA-L_v1.tex
Rewrote introduction, added discussion section on why we don't control directly in embedding space, still need to rewrite Sec. IV

Robot motion planning in joint-space has long been a major field of study \cite{kelly2006control}. For manipulation problems with an objective defined in task space (i.e. target or desired trajectory), we can often find a myriad of joint-space trajectories to achieve the same task-space goal. In many cases, however, certain joint-space trajectories are favored over others; for example, when we expect the robot to follow a desired joint-space behavior or ``style", as illustrated in Fig. \ref{fig:robot_example}.

Learning robot motion generators that follow desired joint and/or task-space behaviors is, in fact, the central focus of Programming by Demonstration (PbD) \cite{billard2008robot} \cite{Argall:RAS:2009}. Historically, much of the original work in PbD focused on learning motions solely in joint-space by parameterizing motions using GMMs \cite{Calinon:HRI:2007}, HMMs \cite{Garrido:Neuro:2015}, GPs \cite{Shon:HUM:2005}, or other probabilistic models \cite{Schaal:IROS:2003,Schaal:AI:2002}. Concurrently, a significant body of work from the graphics community was targeted at learning joint-space motion ``styles" from human motion capture data, through a variety of latent-space and stylistic probabilistic motion models \cite{gielniak2010stylized,grochow2004style}. Yet, over time, research shifted to pure task-space learning \cite{Pastor:ICRA:2009,Gribovskaya:IJRR:2011,Calinon:ISR:2015}, which has two main advantages over pure joint-space: \textit{generalization} and \textit{re-usability}. By learning motions in task-space, one can concisely encode the task-relevant features and generate new motions which meet these task-space criteria. Furthermore, a task-space trajectory is robot-independent, and thus can be reused across robots with differing morphologies.

A major drawback of these initial task-space methods was that despite learning motions similar to the demonstrations, there was no guarantee when applying the learned motion to a new problem (e.g. a different initial/target position) that the end-effector would stably converge to its ultimate task-space target. This led to the introduction and subsequent popularity of task-space learning techniques such as SEDS \cite{khansari2011learning}, $\tau$-SEDS \cite{Neumann:RAS:2015}  and LMDS \cite{Kronander:RAS:2015} which encode task-space behaviors as asymptotically stable dynamical systems (DS) guaranteed to converge towards a desired task-space target.

\begin{figure}[t]
\centering
\includegraphics[scale=.23,trim={0 0 0 0cm},clip]{Without_Obstcle_white_new.png}
\includegraphics[scale=.23,trim={0 0 0 0cm},clip]{With_Obstcle.png}
\caption{Two robot motions in \textcolor{orange}{\textbf{joint-space}} accomplishing \textit{similar} behavior in \textcolor{cyan}{\textbf{task-space}} (pouring chips in a bowl). The bottom example avoids a known obstacle in its workspace, while the top one does not.}
\label{fig:robot_example}
\end{figure}

For all the previously mentioned task-space techniques, the robot is ultimately controlled by projecting the desired task-space velocity into joint-space via Jacobian Pseudo-Inverse based Inverse-Kinematic (IK) approximations and variants thereof \cite{kelly2006control}. When the main focus is on executing a complex task-space behavior, regardless of a specific joint-space constraint, this approach has been deemed sufficient \cite{figueroa2016HRIrolling,ureche2015taskconst}. However, for other applications, such an approach yields significant problems \cite{buss2004introduction}. First of all, finding the pseudo-inverse is computationally taxing. Moreover, when the Jacobian matrix cannot be inverted (i.e. when the robot is near a singularity) its behavior becomes erratic, requiring layers of additional engineering to generate smooth trajectories and ensure the desired task-space behavior. These problems encapsulate the main source of inaccuracies in tasks that require generating fast dynamical motions, such as catching or reaching for moving objects \cite{7439839,Salehian-RSS-16}.

Although DS-based task-space learning techniques ensure target convergence and stability, they still suffer from this reliance on IK methods, possibly generating erratic or discontinuous motions during execution. Further, for certain tasks, rather than generating arbitrary joint-space trajectory returned by the IKs solver, it might be desirable to learn behaviors and ``styles" in joint-space directly.  For example, throwing a ball is a motion less characterized by task-space behaviors (the ball moving backwards and then forwards) and more characterized by the joint behaviors: the elbow folds, the shoulder moves back and then swings forward, followed by the elbow straightening and the wrist snapping down. For a visual example of the need for such combined task/joint-space behavior learning, see Fig. \ref{fig:robot_example}. This is precisely the shortcoming associated with LfD in task-space: it fails to learn the joint-space behavior of the system. The current formulation of the DS-based learning techniques introduced thus far (e.g. SEDS, $\tau$-SEDS LMDS, etc.) do not allow for integrating combined task/joint-space behavior learning.

\subsection{\textcolor{red}{Approaches that tackle the joint+task problem}}
\textcolor{red}{*See comments in tex*}
% TO YO:
% ADD THESE THREE REFERENCES HERE AND SUMMARIZE THEM
%[1] Y. Huang, D. B ̈uchler, O. Koc, B. Scholkopf and J. Peters, “Jointly
%learning trajectory generation and hitting point prediction in robot table
%tennis,” in Proc. IEEE International Conference on Humanoid Robots,
%2016, pp. 650-655.
%
%[2] S. Calinon and A. Billard, “Statistical learning by imitation of competing constraints in joint space and task space,” Advanced Robotics,vol. 23, pp. 2059-2076, 2009.
%
%[3] J. Silverio, S. Calinon, L. Rozo and D. G. Caldwell, “Learning competing constraints and task priorities from demonstrations of bimanual skills,” arXiv:1707.06791, 2017.

\cite{calinon2008probabilistic} notably attempted to address this problem by learning separate motion policies in task space and the null space of the Jacobian (which would not affect task-space position), and driving the robot with a weighted sum of the two. However, this approach no longer guarantees convergence to the desired task-space target and is still reliant on computing the pseudo-inverse Jacobian.

\cite{lee2014unifying} learns from demonstration in both joint and task space within the "thin-plate spline" trajectory warping framework, but does not propose a dynamical system for generating motions.

\subsection{Our proposed Approach}
\textcolor{red}{Dynamical System, Why?\\Linear Parameter Varying, Why?\\Lower-Dimensional Manifold, Why?\\}
In this work, we seek to devise an augmented \textbf{J}oint-space \textbf{T}ask-oriented \textbf{D}ynamical \textbf{S}ystem (JT-DS) that not only incorporates task-space attractors, but also avoids the problems generated by pseudo-inverse approximations. \cite{hersch2008reaching} proposed an approach with similar properties to this desiderata, where two concurrent DS, one in task-space and one in joint-space, are modulated by enforcing kinematic coherence constraints to avoid singularities. The resulting DS avoids singularities through generalization of the pseudo-inverse approximations. However, because the two DS have their own unique attractors, the non-linear interaction between them imposed by the kinematic constraints does not ensure that the combined DS has a unique attractor. This gives rise to spurious attractors or cycles, and thus must be carefully tuned in order to avoid them. In this work, we depart from any modulation or combination of DS and instead propose a novel dynamical system which:

\begin{enumerate}[leftmargin=*]
\item computes a \begin{bf}complex motion in joint space\end{bf} that provably and stably converges to a \begin{bf}fixed task-space target\end{bf}.
\item \textbf{avoids} the need for computing \textbf{pseudo-inverses}, and cleanly moves through kinematic ``singularities".
\item is formulated such that complex \textbf{joint-space behaviors} can be \textbf{learned} from demonstrations in \textbf{synergy space}.
\end{enumerate}

The most similar approach to our proposed DS is the Jacobian transpose (JT) control \cite{wolovich1984computational} method. JT control is an inverse kinematics
method that yields a dynamical system in joint space $\dot{q} = f(q)$ which converges stably (in the sense of Lyapunov) over time to a desired end-effector position $x^*$, without the need for pseudo-inverse computations. It shares some of our approach's advantages: fast computation and provable task-space stability. However, despite some previous work designing velocity adjustments by hand \cite{Shi2016}, this is the first known work to employ a JT system to learn behaviors from demonstrations. 
%while obeying the robots kinematic constraints.

@@

A central question becomes how to modulate the synergies in different regions to yield our desired behavior. First, we assume that our desired behavior can be efficiently described\footnote{Given some original space $A$ and some behavior policy $\pi_A(a)$ in $A$, we say that a latent mapping $\phi(\cdot)$ and latent space $B: \{b = \phi(a) | a \in A\}$ "efficiently describe" $\pi_A$ if there exists some policy $\pi_B(b)$ in $B$ such that we can deterministically reconstruct $\pi_A(a)$ given $\pi_B(\phi(a))$} using some sub-manifold of the joint-space, called the \emph{synergy space}. We would like to define the robot's policy in synergy space such that in different regions of the space, we will utilize different synergies. We are thus left with three problems: finding an underlying synergy-space $Z$ in which the behavior can be accurately controlled (defined by a mapping $\phi: Q \rightarrow Z$), finding a policy for modulating the synergies in different regions of the synergy space (defined by $\theta_k(q)~\forall k\in\{1,\dots,K\}$), and finding parameters for the synergies themselves (defined by $A_k~\forall k\in\{1,\dots,K\}$). Our choice of parameters must also obey the constraints laid out in \eqref{eq:first_criteria_stability}. We propose the following 3-step procedure.

@@

%JTDS can be expanded to incorporate joint limits of the form $q^i_{max} > q^i > q^i_{min}$. Previous work proposed adding discontinuous limits to JT control \cite{sciavicco1988solution}, and we additionally propose a continuous modification as follows: \textcolor{red}{Remove this part? Should we not talk about continuous joint limiting?} Replace the combined synergy matrix $\mathcal{A}(q)$ with a joint-limited joint-behavior matrix $\mathcal{A}_l = S(q)\mathcal{A}(q)S^T(q)$, where $S(q)$ is a bounded positive semidefinite diagonal matrix such that  
%\begin{equation}
%\label{eq:last_criteria}
%\begin{cases}
%\begin{split}
%& s^{i}(q^i_{max}) = 0&&&\\
%& s^{i}(q^i_{min})= 0&&&
%\end{split}
%\forall i\in 1,\dots,m
%\end{cases}
%\end{equation}
%$\mathbb{A}$ is also positive semidefinite, so the system is still provably stable w.r.t. the attractor. The structure of $S$ enforces kinematic joint limits because as a joint nears one of its limits, its magnitude decreases such that it will never actually collide with the limit. One way of constructing $S$ is to use the following function:
%\begin{equation}
%s^{i}(q) =
%1 - \left ( 2\frac{q^i - q^i_{min}}{q^i_{max} - q^i_{min}} - 1 \right ) ^{4}  ~\forall i\in 1,\dots,m\\
%\end{equation}
%The algorithm can similarly be expanded to accommodate joint velocity limits by scaling the controller's velocity down such that the highest-velocity component is still within the velocity limits. Specifically, given some set of velocity constraints for each joint $i$ s.t. $\dot{q}_i < \dot{q}_{i, max}$, we can design a new joint augmentation matrix $\mathcal{A}' = r \mathcal{A}$ where $r = \min \left ( 1, \max_i \left ( \frac{\dot{q}_{i, max}}{\dot{q}_i} \right ) \right )$. This velocity scalar would slow down the joint trajectory when the robot dynamics could not execute them, but would not change the position profile of the joint motion, preserving a major aspect of the joint behavior.

>>>>

Robot motion planning in joint-space has long been a major field of study \cite{kelly2006control}. For manipulation problems with an objective defined in task space (i.e. target or desired trajectory), we can often find a myriad of joint-space trajectories to achieve the same task-space goal. In many cases, however, certain joint-space trajectories are favored over others; for example, when we expect the robot to follow a desired joint-space behavior or ``style", as illustrated in Fig. \ref{fig:robot_example}. In this paper, we will explore the problem of learning a preferred joint-space behavior from previously demonstrated trajectories while still accomplishing a task-space goal, through the Learning from Demonstrations (LfD) paradigm \cite{billard2008robot,Argall:RAS:2009}.

Many LfD approaches learn motions in either joint space \cite{Calinon:HRI:2007, Garrido:Neuro:2015, Schaal:IROS:2003,Schaal:AI:2002} or task space \cite{Pastor:ICRA:2009,Gribovskaya:IJRR:2011,Calinon:ISR:2015}. These approaches generally learn probabilistic model of the demonstrated motions, and construct a dynamical system that chooses behaviors according to the learned model.
Both joint and task space are independently useful: joint-space behaviors let us directly influence the behavior of the physical robot, while task-space behaviors let us control the most task-relevant component of the robot's behavior. In particular, a number of approaches have pioneered stable convergence to an attractor in task space \cite{khansari2011learning, Neumann:RAS:2015, Kronander:RAS:2015} as a desirable capability for a dynamical system.

In many cases, one may want to specify a joint-space behavior while simultaneously fulfilling a task-space objective. For example, throwing a ball is a motion characterized both by a task-space behavior (the ball moves backwards and then forwards) and also more obviously by its joint-space behavior (the elbow folding, the shoulder moving back and then swinging forward, and then the elbow straightening and the wrist snapping down). Similarly, learned joint-space behaviors are helpful in playing ping pong \cite{huang2016jointly}, grasping \cite{calinon2010learning}, and avoiding self-collisions of bimanual manipulators\cite{silverio2017learning}. For a visual example of a task-space problem in which joint behavior is essential, see Fig. \ref{fig:robot_example}.

A second reason for learning a motion in joint space is that this allows us to avoid inverse kinematic (IK) approximations. The previously discussed task-space dynamical systems all rely on projecting the desired task-space velocity into joint-space via Jacobian Pseudo-Inverse based Inverse-Kinematic (IK) approximations and variants thereof \cite{kelly2006control}. When the main focus is on executing a complex task-space behavior, regardless of a specific joint-space constraint, this approach has been deemed sufficient \cite{figueroa2016HRIrolling,ureche2015taskconst}. However, for other applications, such an approach yields significant problems \cite{buss2004introduction}. First of all, finding the pseudo-inverse is computationally taxing. Moreover, when the Jacobian matrix cannot be inverted (i.e. when the robot is near a singularity) its behavior becomes erratic, requiring layers of additional engineering to generate smooth trajectories and ensure the desired task-space behavior. These problems encapsulate the main source of inaccuracies in tasks that require generating fast dynamical motions, such as catching or reaching for moving objects \cite{7439839,Salehian-RSS-16}. By defining a controller in joint space directly, one can avoid IK and all its associated drawbacks.
%Further, for certain tasks, rather than generating arbitrary joint-space trajectory returned by the IKs solver, it might be desirable to learn behaviors and ``styles" in joint-space directly.  For example, throwing a ball is a motion less characterized by task-space behaviors (the ball moving backwards and then forwards) and more characterized by the joint behaviors: the elbow folds, the shoulder moves back and then swings forward, followed by the elbow straightening and the wrist snapping down. For a visual example of the need for such combined task/joint-space behavior learning, see Fig. \ref{fig:robot_example}.
%In this work, we propose a method for learning a joint-space dynamical system that learns behaviors from demonstrations in joint space, while provably converging to an attractor in task space.
%For all the previously mentioned task-space techniques, the robot is ultimately controlled by projecting the desired task-space velocity into joint-space via Jacobian Pseudo-Inverse based Inverse-Kinematic (IK) approximations and variants thereof \cite{kelly2006control}. When the main focus is on executing a complex task-space behavior, regardless of a specific joint-space constraint, this approach has been deemed sufficient \cite{figueroa2016HRIrolling,ureche2015taskconst}. However, for other applications, such an approach yields significant problems \cite{buss2004introduction}. First of all, finding the pseudo-inverse is computationally taxing. Moreover, when the Jacobian matrix cannot be inverted (i.e. when the robot is near a singularity) its behavior becomes erratic, requiring layers of additional engineering to generate smooth trajectories and ensure the desired task-space behavior. These problems encapsulate the main source of inaccuracies in tasks that require generating fast dynamical motions, such as catching or reaching for moving objects \cite{7439839,Salehian-RSS-16}.
%Historically, much of the original work in LfD focused on learning motions solely in joint-space by parameterizing motions using GMMs \cite{Calinon:HRI:2007}, HMMs \cite{Garrido:Neuro:2015}, GPs \cite{Shon:HUM:2005}, or other probabilistic models \cite{Schaal:IROS:2003,Schaal:AI:2002}. Concurrently, a significant body of work from the graphics community was targeted at learning joint-space motion ``styles" from human motion capture data, through a variety of latent-space and stylistic probabilistic motion models \cite{gielniak2010stylized,grochow2004style}. Yet, over time, research shifted to pure task-space learning \cite{Pastor:ICRA:2009,Gribovskaya:IJRR:2011,Calinon:ISR:2015}, which has two main advantages over pure joint-space: \textit{generalization} and \textit{re-usability}. By learning motions in task-space, one can concisely encode the task-relevant features and generate new motions which meet these task-space criteria. Furthermore, a task-space trajectory is robot-independent, and thus can be reused across robots with differing morphologies.
%A major drawback of these initial task-space methods was that despite learning motions similar to the demonstrations, there was no guarantee when applying the learned motion to a new problem (e.g. a different initial/target position) that the end-effector would stably converge to its ultimate task-space target. This led to the introduction and subsequent popularity of task-space learning techniques such as SEDS \cite{khansari2011learning}, $\tau$-SEDS \cite{Neumann:RAS:2015}  and LMDS \cite{Kronander:RAS:2015} which encode task-space behaviors as asymptotically stable dynamical systems (DS) guaranteed to converge towards a desired task-space target.

\begin{figure}[t]
\centering
\includegraphics[scale=.23,trim={0 0 0 0cm},clip]{Without_Obstcle_white_new.png}
\includegraphics[scale=.23,trim={0 0 0 0cm},clip]{With_Obstcle.png}
\caption{Two robot motions in \textcolor{orange}{\textbf{joint-space}} accomplishing \textit{similar} behavior in \textcolor{cyan}{\textbf{task-space}} (pouring chips in a bowl). The bottom example avoids a known obstacle in its workspace, while the top one does not.}
\label{fig:robot_example}
\end{figure}
%For all the previously mentioned task-space techniques, the robot is ultimately controlled by projecting the desired task-space velocity into joint-space via Jacobian Pseudo-Inverse based Inverse-Kinematic (IK) approximations and variants thereof \cite{kelly2006control}. When the main focus is on executing a complex task-space behavior, regardless of a specific joint-space constraint, this approach has been deemed sufficient \cite{figueroa2016HRIrolling,ureche2015taskconst}. However, for other applications, such an approach yields significant problems \cite{buss2004introduction}. First of all, finding the pseudo-inverse is computationally taxing. Moreover, when the Jacobian matrix cannot be inverted (i.e. when the robot is near a singularity) its behavior becomes erratic, requiring layers of additional engineering to generate smooth trajectories and ensure the desired task-space behavior. These problems encapsulate the main source of inaccuracies in tasks that require generating fast dynamical motions, such as catching or reaching for moving objects \cite{7439839,Salehian-RSS-16}. 
%Although DS-based task-space learning techniques ensure target convergence and stability, they still suffer from this reliance on IK methods, possibly generating erratic or discontinuous motions during execution. Further, for certain tasks, rather than generating arbitrary joint-space trajectory returned by the IKs solver, it might be desirable to learn behaviors and ``styles" in joint-space directly.  For example, throwing a ball is a motion less characterized by task-space behaviors (the ball moving backwards and then forwards) and more characterized by the joint behaviors: the elbow folds, the shoulder moves back and then swings forward, followed by the elbow straightening and the wrist snapping down. For a visual example of the need for such combined task/joint-space behavior learning, see Fig. \ref{fig:robot_example}. This is precisely the shortcoming associated with LfD in task-space: it fails to learn the joint-space behavior of the system. The current formulation of the DS-based learning techniques introduced thus far (e.g. SEDS, $\tau$-SEDS LMDS, etc.) do not allow for integrating combined task/joint-space behavior learning.

\subsection{Prior Work on Combined Joint and Task Space Control}
\textcolor{red}{*See comments in tex*}
% TO YO:
% ADD THESE THREE REFERENCES HERE AND SUMMARIZE THEM
%[1] Y. Huang, D. B ̈uchler, O. Koc, B. Scholkopf and J. Peters, “Jointly
%learning trajectory generation and hitting point prediction in robot table
%tennis,” in Proc. IEEE International Conference on Humanoid Robots,
%2016, pp. 650-655.
%
%[2] S. Calinon and A. Billard, “Statistical learning by imitation of competing constraints in joint space and task space,” Advanced Robotics,vol. 23, pp. 2059-2076, 2009.
%
%[3] J. Silverio, S. Calinon, L. Rozo and D. G. Caldwell, “Learning competing constraints and task priorities from demonstrations of bimanual skills,” arXiv:1707.06791, 2017.

\cite{calinon2008probabilistic} notably attempted to address this problem by learning separate motion policies in task space and the null space of the Jacobian (which would not affect task-space position), and driving the robot with a weighted sum of the two.  However, this approach does not seek convergence to the desired task-space target and is still reliant on computing the pseudo-inverse Jacobian. \cite{calinon2010learning} and \cite{silverio2017learning} expand on this approach by projecting task-space constraints into joint space using IK, and then learning a joint-space policy that incorporates both task and joint space constraints, but this similarly relies on IK approximations and does not ensure convergence to an attractor.
% FACT-CHECK: is this what Calinon 2009 and Silverio et al. 2017 are doing? They don't ensure convergence, right? TP-GMM never seems to address it

\cite{lee2014unifying} learns from demonstration in both joint and task space within the "thin-plate spline" trajectory warping framework, but does not propose a dynamical system for generating motions. 
\cite{huang2016jointly} learns a controller for playing table tennis by combining joint-space Dynamic Movement Primitives \cite{schaal2006dynamic} to mimic a desired task-space racket swing, but does not learn joint-space behaviors.
% Do DMPs count as learning joint space behaviors? If yes, I'm having a hard time differentiating huang2016 from us.

\cite{hersch2008reaching} proposed an approach with similar properties to this desiderata, where two concurrent DS, one in task-space and one in joint-space, are modulated by enforcing kinematic coherence constraints to avoid singularities. The resulting DS avoids singularities through generalization of the pseudo-inverse approximations. However, because the two DS have their own unique attractors, the non-linear interaction between them imposed by the kinematic constraints does not ensure that the combined DS has a unique attractor. This gives rise to spurious attractors or cycles, and thus must be carefully tuned in order to avoid them.

\subsection{Our Proposed Approach}
In this work, we seek to devise an augmented \textbf{J}oint-space \textbf{T}ask-oriented \textbf{D}ynamical \textbf{S}ystem (JT-DS) that not only incorporates task-space attractors, but also avoids the problems generated by pseudo-inverse approximations. We specifically chose to focus on linear parameter-varying dynamical systems because they are fast to compute and thus allow a controller to quickly react in a changing environment, a capability that is further improved by our not needing to compute pseudo-inverses. Our dynamical system:
\begin{enumerate}[leftmargin=*]
\item computes a \begin{bf}complex motion in joint space\end{bf} that provably and stably converges to a \begin{bf}fixed task-space target\end{bf}.
\item \textbf{avoids} the need for computing \textbf{pseudo-inverses}, and cleanly moves through kinematic ``singularities".
\item is formulated such that complex \textbf{joint-space behaviors} can be \textbf{learned} from demonstrations in \textbf{synergy space}.
\end{enumerate}
In brief, our algorithm learns a set of \emph{behavior synergies}, each of which corresponds to a different provably stable behaviors in joint space, and modulates the use of these synergies throughout joint-space using a learned LPV system. We determine the scheduling parameters for the LPV by finding a \emph{lower-dimensional embedding} of the joint space, which accounts for the variation in the demonstrated motions, and then learning a policy in embedding space for combining our behavior synergies to accurately reconstruct the demonstrated trajectories.

The most similar approach to our proposed DS is the Jacobian transpose (JT) control \cite{wolovich1984computational} method. JT control is an inverse kinematics method that yields a dynamical system in joint space $\dot{q} = f(q)$ which converges stably (in the sense of Lyapunov) over time to a desired end-effector position $x^*$, without the need for pseudo-inverse computations. It shares some of our approach's advantages: fast computation and provable task-space stability. However, despite some previous work designing velocity adjustments by hand \cite{Shi2016}, this is to the best of our knowledge the first work to employ a JT system to learn behaviors from demonstrations. 
%while obeying the robots kinematic constraints.

@@

A central question becomes how to modulate the synergies in different regions to yield our desired behavior. First, we assume that our desired behavior can be efficiently described\footnote{Given some original space $A$ and some behavior policy $\pi_A(a)$ in $A$, we say that an embedding $\phi(\cdot)$ and embedding space $B: \{b = \phi(a) | a \in A\}$ "efficiently describe" $\pi_A$ if there exists some policy $\pi_B(b)$ in $B$ such that we can deterministically reconstruct $\pi_A(a)$ given $\pi_B(\phi(a))$} using some sub-manifold of the joint-space, called the \emph{synergy space}. We would like to define the robot's policy in synergy space such that in different regions of the space, we will utilize different synergies. We are thus left with three problems: finding an underlying synergy-space $Z$ in which the behavior can be accurately controlled (defined by a mapping $\phi: Q \rightarrow Z$), finding a policy for modulating the synergies in different regions of the synergy space (defined by $\theta_k(q)~\forall k\in\{1,\dots,K\}$), and finding parameters for the synergies themselves (defined by $A_k~\forall k\in\{1,\dots,K\}$). Our choice of parameters must also obey the constraints laid out in \eqref{eq:first_criteria_stability}. We propose the following 3-step procedure.

@@

Since we learn a lower-dimensional embedding space $Z := \{\phi(q) ~|~q \in Q\}$, which we suggest provides a better representation for the learned joint behaviors, a careful reader might wonder: why not define a motion policy $\pi_Z$ directly in $Z$-space and then map the learned policy back out into joint space using the inverse embedding\footnote{Such an inverse is trivial to extract in the case where $\phi$ is obtained through PCA.} $\phi^{-1}(z)$? The answer is that we would lose any guarantee of stability with respect to a target attractor $x_t$. By construction, $\phi$ maps from a joint-position vector of size $d$ to a low-dimensional vector of size $u<d$. Thus the inverse $\phi^{-1}$ must be of less than full rank, so the resulting $\mathcal{A}$ matrix (derived as in \eqref{eq:ds}) will also be of less than full rank, and thus no longer positive definite. This means that our controller no longer provably converges to the attractor (since our convergence proof no longer holds). Intuitively, this is because any policy defined in a lower-dimensional space than the actuation space will forfeit certain degrees of freedom, and thus may not be able to span the configuration space. Instead, we use the embedding space to modulate synergies defined in joint space, and which we can thus guarantee will be positive definite and lead us to convergence to the target.
%JTDS can be expanded to incorporate joint limits of the form $q^i_{max} > q^i > q^i_{min}$. Previous work proposed adding discontinuous limits to JT control \cite{sciavicco1988solution}, and we additionally propose a continuous modification as follows: \textcolor{red}{Remove this part? Should we not talk about continuous joint limiting?} Replace the combined synergy matrix $\mathcal{A}(q)$ with a joint-limited joint-behavior matrix $\mathcal{A}_l = S(q)\mathcal{A}(q)S^T(q)$, where $S(q)$ is a bounded positive semidefinite diagonal matrix such that  
%\begin{equation}
%\label{eq:last_criteria}
%\begin{cases}
%\begin{split}
%& s^{i}(q^i_{max}) = 0&&&\\
%& s^{i}(q^i_{min})= 0&&&
%\end{split}
%\forall i\in 1,\dots,m
%\end{cases}
%\end{equation}
%$\mathbb{A}$ is also positive semidefinite, so the system is still provably stable w.r.t. the attractor. The structure of $S$ enforces kinematic joint limits because as a joint nears one of its limits, its magnitude decreases such that it will never actually collide with the limit. One way of constructing $S$ is to use the following function:
%\begin{equation}
%s^{i}(q) =
%1 - \left ( 2\frac{q^i - q^i_{min}}{q^i_{max} - q^i_{min}} - 1 \right ) ^{4}  ~\forall i\in 1,\dots,m\\
%\end{equation}
%The algorithm can similarly be expanded to accommodate joint velocity limits by scaling the controller's velocity down such that the highest-velocity component is still within the velocity limits. Specifically, given some set of velocity constraints for each joint $i$ s.t. $\dot{q}_i < \dot{q}_{i, max}$, we can design a new joint augmentation matrix $\mathcal{A}' = r \mathcal{A}$ where $r = \min \left ( 1, \max_i \left ( \frac{\dot{q}_{i, max}}{\dot{q}_i} \right ) \right )$. This velocity scalar would slow down the joint trajectory when the robot dynamics could not execute them, but would not change the position profile of the joint motion, preserving a major aspect of the joint behavior.
